---
title: "Live Coding with typeR"
subtitle: "Interactive Demonstrations for Presentations"
author: "Your Name"
format: 
  revealjs:
    theme: default
    transition: slide
    incremental: false
---

## Introduction

Welcome to this live coding demonstration!

::: {.notes}
This presentation demonstrates how typeR works with Quarto reveal.js presentations.
:::

## Simple Data Analysis

```{r}
# Create sample data
x <- 1:10
y <- x * 2

# Calculate summary statistics
mean(x)
sum(y)
```

## Visualization

```{r}
# Create a simple plot
plot(x, y, 
     main = "Linear Relationship",
     xlab = "X values", 
     ylab = "Y values",
     pch = 19, 
     col = "steelblue")

# Add a line
abline(lm(y ~ x), col = "red", lwd = 2)
```

## Working with Data Frames

```{r}
# Load built-in dataset
data(mtcars)

# Show structure
str(mtcars)

# Basic summary
summary(mtcars$mpg)
```

## Statistical Analysis

```{r}
# Fit a linear model
model <- lm(mpg ~ wt + hp, data = mtcars)

# View the summary
summary(model)
```

## Data Manipulation

```{r}
# Filter high efficiency cars
efficient_cars <- mtcars[mtcars$mpg > 25, ]

# Show results
head(efficient_cars)
```

## Thank You!

Questions?

::: {.notes}
This slide deck can be used with typeRun() to create live coding demonstrations
in Quarto presentations.
:::
